---
title: "Assignment 2"
output:
  html_document:
    df_print: paged
---

### Load the library

Install the `rvest` package if it is not yet installed

```{r}
if (!("rvest" %in% installed.packages())) {
  install.packages("rvest")
}
library(rvest)  # import the 'rvest' package
```

### Get the csv example

Load in the html, from the url specified, as html nodes/docs object.

```{r}
wiki_url <- "https://en.wikipedia.org/wiki/Comma-separated_values"
wiki_html <- read_html(wiki_url)
wiki_html
```

Get the csv examples under the header "Example". <br>
Locate where the header "Example" with id='Example' is.

%>% is piping, where left hand side output/result is pass to right hand side functions to process.

```{r}
csv_lst <- 
  wiki_html %>% 
  html_nodes(xpath="//table[contains(@class,'wikitable')]//following-sibling::pre") %>%
  html_text()

#csv_lst <- 
#  wiki_html %>% 
#  html_nodes(xpath="//h2[contains(.,'Example')]/following-sibling::pre") %>%
#  html_text()
```

Have a look of the tables:

```{r}
csv_lst
```

The first element is what we want.

```{r}
csv_text <- csv_lst[1]
```

### Save the csv example into a csv file

```{r}
write.table(csv_text, file = "car.csv", quote = FALSE, col.names = FALSE, row.names = FALSE)
```

Reload the csv data from the file to make sure the data was saved properly

```{r}
read.csv("car.csv")
```
